%-------------------------
% Resume in LateX
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Nicola Scionti} & Email: \href{mailto:nicolascionti.dev@gmail.com}{nicolascionti.dev@gmail.com}\\
  Full Stack Engineer
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Milano-Bicocca}{Milano, MI, Italy}
      {Master's Degree in Computer Science}{Graduated: 2020}
    \resumeSubheading
      {University of Milano-Bicocca}{Milano, MI, Italy}
      {Bachelor's Degree in Physics}{Graduated: 2017}
  \resumeSubHeadingListEnd



  \section{Overview}
  I am a first-principle thinker who loves challenges and solving difficult problems.
  I hold strong opinions, but I'm always ready to change them when presented with new evidence.
  This mindset has helped me build a strong problem-solving framework while staying adaptable to changing boundary conditions.
  In the first five years of my career, I prioritized developing a broad understanding of the overall product over specializing deeply in one area. For this reason, I identify as a Full Stack Engineer.
  I am most experienced in the TypeScript ecosystem but am always open to exploring other technologies, whether for work or personal projects.

%-----------EXPERIENCE-----------------
\section{Freelancing Experience}


  \resumeSubHeadingListStart

    \resumeSubheading
      {\href{https://www.oaks.cloud/}{OAKS}}{Remote}
      {Full Stack Engineer}{2020 -- Present}
      \resumeItemListStart
        
      \resumeItem{Analytic Dashboard}
          {A business intelligence dashboard designed to analyze the customer experience at Leroy Merlin. The data comes primarily from surveys, which are aggregated to present both well-known indicators like the Net Promoter Score and custom KPIs that emphasize specific business aspects. A classifier is also implemented to categorize feedback from customers. }
          \resumeItemListStart
            \resumeItem{Stack}{Postgres, NestJS, Angular, Kubernetes}
          \resumeItemListEnd

        \resumeItem{\href{https://custory.it/}{Analytic Dashboard}}
          {Generalization of the previously described dashboard, with the aim to target all types of businesses, having data stored in various structures.}
            \resumeItemListStart
              \resumeItem{Stack}{Postgres, Next.js}
            \resumeItemListEnd

          \resumeItem{Chrome Extension}
          {A tool to record and replicate user interactions with the web page.}
            \resumeItemListStart
              \resumeItem{Stack}{React}
            \resumeItemListEnd
          \resumeItemListEnd
      

    \resumeSubheading
      {\href{https://forest-fire.emergency.copernicus.eu/}{EFFIS} - Arcadia}{Remote + JRC Ispra, VA}
      {Full Stack Engineer}{2023 -- Present}
      \resumeItemListStart
        \resumeItem{\href{https://forest-fire.emergency.copernicus.eu/apps/effis.csv/}{Current Situation Viewer}}
          {An interactive map that shows the most up-to-date information on the current fire season in Europe and the Mediterranean area. This includes today's meteorological fire danger maps and forecasts for up to 6 days, as well as daily updated maps of hot spots and fire perimeters.}
          \resumeItemListStart
            \resumeItem{Stack}{Postgres, Flask, Vue, Kubernetes}
          \resumeItemListEnd
        \resumeItem{\href{https://forest-fire.emergency.copernicus.eu/apps/dss.test/}{Decision Support System}}
          {An interactive map that visualizes wildfires and their severity, while also displaying real-time data on the location and type of firefighting resources.}
          \resumeItemListStart
            \resumeItem{Stack}{Postgres, Flask, Vue, Kubernetes}
          \resumeItemListEnd
        \resumeItem{Workflows}
          {Engineered scientific scripts that compute data for the previous two applications, then containerized, scheduled, and deployed them.}
          \resumeItemListStart
            \resumeItem{Stack}{Gitlab CI/CD}
          \resumeItemListEnd
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://quantaste.com/en/}{Quantaste}}{Remote}
      {Full Stack Engineer}{2022 -- 2023}
      \resumeItemListStart
        \resumeItem{\href{https://quantaste.com/en/auth/sign-in}{Financial Dashboard}}
          {Product used to track financial data, create portfolios and analize them from a correlation perspective.}
          \resumeItemListStart
            \resumeItem{Stack}{Postgres, Flask, Next.js, AWS}
          \resumeItemListEnd
      \resumeItemListEnd

 
  \resumeSubHeadingListEnd





%-----------PROJECTS-----------------
\section{Personal Projects}
  \resumeItemListStart
    \resumeItem{\href{https://stockthatcheddar.com/}{Stock That Cheddar}}
      {Aims to be a platform that supports people in managing all aspects of personal finance, including cash flow monitoring, portfolio management, and net worth tracking.}
      \resumeItemListStart
        \resumeItem{Stack}{Postgres, Golang, Sveltekit}
      \resumeItemListEnd
  \resumeItemListEnd

%-------------------------------------------
\end{document}